Laplacian envelope

### 2021-08-27 Notes/laplace.tex
changimg units

If the plasticity events occur at Poisson rate \(r\), the probability of \(n\) events occurring in time \(t\) is given by a Poisson distribution with mean \(rt\).
If we marginalise over \(n\) as well
%
\begin{equation}\label{eq:plastseqav}
\begin{aligned}
  P(\text{state}=i,t \mid \text{pot/dep},0)
    &= \sum_n \frac{(rt)^n}{n!} \e^{-rt} \eq  \MMd \potdep (f\pot \MMd \pot+f\dep \MMd \dep)^n \\
    &= \brk{ \eq  \MMd \potdep\, \e^{rt(f\pot \MMd \pot+f\dep \MMd \dep-\I) } }_i,
\end{aligned}
\end{equation}
%
where \(\eq\) is the steady state distribution of the continuous time transition matrix that appears in the exponential:
%
\begin{equation}\label{eq:eq}
  \eq\frg = 0,
  \qquad\text{where}\quad
  \frg = \sum_\nu f^\nu \MMd^\nu - \I
    = f\pot \MMd \pot + f\dep \MMd \dep - \I.
\end{equation}
%

This results in
%
\begin{equation}\label{eq:overlapwt}
\begin{aligned}
  \av{\synid^1 \syn^1(t)} &= \eq (f\pot \MMd \pot-f\dep \MMd \dep)\, \e^{rt\frg} \w, \\
  \av{\synid^1 \syn^1(\infty)} &= \eq (f\pot \MMd \pot-f\dep \MMd \dep)\, \onev\eq \w \\
         &= \eq (f\pot\onev-f\dep\onev)\, \eq \w \\
         &=  (f\pot-f\dep)\, \eq \w \\
         &=  \Delta f\, \eq \e^{rt\frg} \w ,
\end{aligned}
\end{equation}
%
where \(\Delta f = f\pot - f\dep \).
Combining the expressions in \cref{eq:overlapwt} allows us to write the numerator of \cref{eq:SNRdef} as
%
\begin{equation}\label{eq:signal}
\begin{aligned}
  \av{\synid \cdt \syn(t)} - \av{\synid \cdt \syn(\infty)}
    &= N \eq \enc \, \e^{rt \frg} \w , \\
    \text{where} \qquad
  \enc &= \sum_\nu (-1)^\nu f^\nu (\MMd^\nu - \I)
    = f\pot(\MMd \pot-\I)-f\dep(\MMd \dep-\I)
\end{aligned}
\end{equation}
%
Combining with \eqref{eq:noise} gives
%
\begin{equation}\label{eq:SNRcurveExact}
  \SNR(t) = \frac{\sqrt{N} \eq \enc\,\e^{rt \frg}\w}
                 {\sqrt{1-(\Delta f)^2(\eq \w)^2}}.
\end{equation}
%
The denominator will not play any role in what follows, as the models that maximize the various measures of memory performance all have some sort of balance between potentiation and depression, either with \(f\pot=f\dep\) or \(\eq_+=\eq_-\).
We can perform the maximisation in two steps.
First maximise the numerator at fixed \(\eq \w\).
Then maximise the ratio \wrt \(\Delta \pr = \eq\w\).
This will allow us to ignore the denominator until the very end.

We can then treat the off-diagonal elements of \(\MMd^\nu\) as the independent degrees of freedom, subject to these constraints, when maximising the SNR.
The diagonal elements are determined by setting the row sums to 1.
We then have
%
\begin{equation}\label{eq:derivpd}
  \pdiff{\MMdm^\mu_{ij}}{\MMdm^\nu_{mn}} 
      = \delta_{\mu\nu}\, \delta_{im}(\delta_{jn}-\delta_{jm}),
\end{equation}
%
It will also be convenient to define the differential operators
%
\begin{equation}\label{eq:pertfe}
  \pdiff{}{\frgm_{ij}} = \frac{1}{2f\pot} \pdiff{}{\MMdm \pot_{ij}} + \frac{1}{2f\dep} \pdiff{}{\MMdm \dep_{ij}},
  \qquad
  \pdiff{}{\encm_{ij}} = \frac{1}{2f\pot} \pdiff{}{\MMdm \pot_{ij}} - \frac{1}{2f\dep} \pdiff{}{\MMdm \dep_{ij}},
\end{equation}
%
these satisfy
%
\begin{equation}\label{eq:derivfe}
  \pdiff{\frgm_{ij}}{\frgm_{mn}} = \pdiff{\encm_{ij}}{\encm_{mn}} = \delta_{im}(\delta_{jn}-\delta_{jm}),
  \qquad
  \pdiff{\frgm_{ij}}{\encm_{mn}} = \pdiff{\encm_{ij}}{\frgm_{mn}} = 0.
\end{equation}
%

If we wish to use the off-diagonal elements of \(\frg\) and \(\enc\) as the degrees of freedom, the constraints are
%
\begin{equation}\label{eq:constrfe}
\begin{aligned}
  \frgm_{i \neq j}   &\geq \abs{ \encm_{i \neq j} }, &\qquad
  \sum_{j\neq i}\frgm_{ij} + (-1)^\mu \encm_{ij}  &\leq 2f^\mu, \\
  \sum_j \frgm_{ij} &=0, &
  \sum_j \encm_{ij} &=0.
\end{aligned}
\end{equation}
%

@@

Now consider the Laplace transform of the SNR curve \eqref{eq:SNRcurveExact}
%
\begin{equation}\label{eq:lsnr}
\begin{aligned}
  A(s) = \intd[_0^{\infty}]{t} \e^{-st}\SNR(t) 
   &= \intd[_0^{\infty}]{t} \frac{ \sqrt{N} \eq \enc \e^{(r\frg-s)t} \w }
                                { \sqrt{1-(\Delta f)^2(\eq\w)^2} } \\
   &= \frac{\sqrt{N} \eq \enc \prn{s \I - r\frg}\inv \w }{\sqrt{1-(\Delta f)^2(\eq\w)^2}}.
\end{aligned}
\end{equation}
%
This expression is ill-behaved at \(s=0\).
Thanks to \eqref{eq:alfund}, we can solve this by the replacement \(\mathbf{G}(s) \to \fund(s)\), as \(\enc\onev=0\).
%
\begin{equation}\label{eq:larea}
\begin{aligned}
  \hat{A}(s) = A(s) \sqrt{\frac{{{1-(\Delta f)^2(\eq\w)^2}}}{N}}  &=  \eq \enc \fund(s) \w \\
    &= \sum_{ijk} \eqm_i \encm_{ij} \prn{\fptbm_{ik}(s)-\fptbm_{jk}(s)} \eqm_k \wm_k \\
    &= \sum_{ij}  \eqm_i \encm_{ij} (\etwm_{i}(s) - \etwm_{j}(s)).
\end{aligned}
\end{equation}
%
Note that \(A(0)=A\), the area, and \(\lim_{s\to\infty} \brc{sA(s)} = \SNR(0)\), the initial SNR.

@@

In analogy with the case \(s=0\) in \cite{Lahiri2013synapse}, we define
%
\begin{equation}\label{eq:lareacoeffs}
  \begin{aligned}
    {c}_k(s) &= r\sum_{ij} \eqm_i \encm_{ij} \prn{\fptbm_{ik}(s)-\fptbm_{jk}(s)}, \\
    {a}_j(s) &= r\sum_{k} \encm_{jk} (\etwm_{j}(s) - \etwm_{k}(s)), \\
    \thbm_i(s) &= \sum_j \fptbm_{ij}(0)\, \eqm_j {a}_j(s), \\
  \end{aligned}
    \implies
    \hat{A}(s) 
      % = \sum_k \eqm_k {c}_k(s) \wm_k
      = \mathbf{c}^\dag(s) \w
      = \eq \mathbf{a}(s).
\end{equation}
%
If we regard the \(\wm_k\) as optimisable parameters (limited to the range \( [-1,1] \) wlg.),s the optimal choice is clearly \( \wm_k = \sgn(c_k) \).

Using the same approach as the area bound in \cite{Lahiri2013synapse} we find that the derivatives are
%
\begin{equation}\label{eq:lAdiff}
  \pdiff{\hat{A}(s)}{\MMdm^\mu_{mn}}
     = f^\mu \eqm_m \prn{ \brk{\thbm_m(s) - \thbm_n(s)}
     +\prn{{c}_m(s) + (-1)^\mu} \brk{\etwm_m(s) - \etwm_n(s)} }.
\end{equation}
%
The term with \(\thb(s)\) comes from differentiating \(\eq\), the term with \(c(s)\) comes from differentiating \(\etw(s)\) and the term with \((-1)^\mu\) comes from differentiating \(\enc\) in \eqref{eq:larea}.

To write down the Hessian, we will first define some notation.
We define the matrix \(\mathbf{X}(s) = r\fund(0) \enc \fund(s)\).
Given a four-index array \(H_{ijkl}\), we define \(H\trans_{ijkl} = H_{klij}\).
Then we denote
%
\begin{equation}\label{eq:hessparts}
\begin{alignedat}{2}
    R_{ijkl} &= \smash{\pdiff{\hat{A}}{\frgm_{ij} \circ ; \frgm_{kl}}} &
    &=
    \eqm_i \brc{\fundm_{ik}(0) - \fundm_{jk}(0)} \brc{\thbm_k(s) - \thbm_l(s)} \\
    &&&\hphantom{=} {}
    + \eqm_i \brc{{X}_{ik}(s) - {X}_{jk}(s)} 
          \brc{\etwm_k(s) - \etwm_l(s)} \\
    &&& \hphantom{=} {}
    + \eqm_i {c}_i(s) \brc{\fundm_{ik}(s) - \fundm_{jk}(s)} 
          \brc{\etwm_k(s) - \etwm_l(s)},  \\
  S_{ijkl} &= \smash{\pdiff{\hat{A}}{\encm_{ij} ; \frgm_{kl}} } &
  &= \eqm_k \brc{\fundm_{ki}(0) - \fundm_{li}(0)} \brc{\etwm_i(s) - \etwm_j(s)} \\
    &&& \hphantom{=} {}
    + \eqm_i \brc{\fundm_{ik}(s) - \fundm_{jk}(s)} \brc{\etwm_k(s) - \etwm_l(s)},
\end{alignedat}
\end{equation}
%
where \(R\) contains only those terms where \( \frgm_{ij} \) precedes \( \frgm_{kl} \) in the matrix products from the expression for \( \hat{A} \) in \cref{eq:larea}.
The missing terms sum to \(R\trans\).

Then we can write the Hessian as
%
\begin{equation}\label{eq:hessian}
  \pdiff{^2\hat{A}(s)}{\MMdm^\mu_{ij} \partial \MMdm^\nu_{kl}} =
     f^\mu f^\nu [R + R\trans + (-1)^\mu S + (-1)^\nu S\trans]_{ijkl}.
\end{equation}
%
This is useful in numerical maximisation.

@@

Consider the Lagrangian
%
\begin{equation}\label{eq:finitelagrangian}
\begin{aligned}
  \CL =&\, \sum_{ij} \eqm_i \encm_{ij} (\etwm_i(s) - \etwm_j(s))
        +\sum_{\nu i j} { f^\nu \mu^\nu_{ij} \MMdm^\nu_{ij} }
        + \lambda \prn{ \Delta\pr - \sum_i \eqm_i \wm_i },
\end{aligned}
\end{equation}
%
where \(\Delta\pr\) is the constant value we are holding \(\eq\w\) at.
The Karush-Kuhn-Tucker necessary conditions for a maximum are
%
\begin{equation}\label{eq:KTfinite}
  \pdiff{\CL}{\MMdm^\nu_{ij}} = 0, \quad
  \mu^\nu_{ij} \geq 0, \quad
  \pdiff{\CL}{\mu^\nu_{ij}} \geq 0, \quad
  \mu^\nu_{ij}\pdiff{\CL}{\mu^\nu_{ij}} = 0, \quad
  \pdiff{\CL}{\lambda} = 0.
\end{equation}
%
We have scaled the KKT multipliers by \(f^\nu\) for later convenience.

The derivatives, for \(m \neq n\) are
%
\begin{equation}\label{eq:finitederivs}
\begin{aligned}
  \frac{1}{f^\nu} \pdiff{\CL}{\MMdm^\nu_{mn}} = & \,
    \eqm_m \prn{ \brk{\thbm_m(s) - \thbm_n(s)}
     + \prn{c_m(s) + (-1)^\nu} \brk{\etwm_m(s) - \etwm_n(s)} } \\
     &+ \mu^\nu_{mn} -  \mu^\nu_{mm}
     + \lambda \eqm_m (\etwm_{m}(0)-\etwm_{n}(0)) 
    = 0.
\end{aligned}
\end{equation}
%
We can solve for the KKT multipliers by noting that
%
\begin{equation*}
  \mu^\nu_{ij} \MMdm^\nu_{ij} = 0,
  \qquad \text{and} \qquad
  \sum_{j: j \neq i} \mu^\nu_{ii} \MMdm^\nu_{ij} 
      = \mu^\nu_{ii} (1 - \MMdm^\nu_{ii}) = \mu^\nu_{ii}.
\end{equation*}
%
Then, with some new vectors defined:
%
\begin{equation}\label{eq:kktsol}
\begin{aligned}
  \mu^\nu_{mm} &= - \eqm_m \prn{ \albm^\nu_m(s) 
    + \lambda \ombm^\nu_m(0) 
    + \prn{{c}_m(s) + (-1)^\nu} \ombm^\nu_m(s)
    }, \\
  \mu^\nu_{mn} &= \eqm_m \big( 
      \brk{ \thbm_n(s) - \thbm_m(s) - \albm^\nu_m(s) }
    + \lambda \brk{ \etwm_n(0) - \etwm_m(0) - \ombm^\nu_m(0) } 
  \\ &\hphantom{= \eqm_m \big( }
    + \brk{{c}_m(s) + (-1)^\nu} 
        \brk{ \etwm_n(s) - \etwm_m(s) - \ombm^\nu_m(s) }
     \big), \\
  \text{where} \quad 
  \alb^\nu(s) &= (\MMd^\nu - \I) \thb(s), \qquad
  \omb^\nu(s) = (\MMd^\nu - \I) \etw(s).
\end{aligned}
\end{equation}
%
If we note that we can write \( \MMd^\nu - \I = \prn{\frg + (-1)^\nu \enc} / 2f^\nu \), we find that
%
\begin{equation}\label{eq:diagKKT}
\begin{aligned}
  \alb^\nu(s) &= \frac{\delta\mathbf{a}(s) + (-1)^\nu \enc \thb(s)}
                     {2f^\nu},
  \qquad 
  \omb^\nu(s) = \frac{\delta\w + s \delta\etw(s) - (-1)^\nu \mathbf{a}(s)}
                     {2 f^\nu}, 
  \\
  \mu^\nu_{mm} &= \frac{\eqm_m}{2f^\nu} 
    \left[ 
      \hat{A}(s) - c_m(s) (\delta\wm_m + s \delta\etwm_m(s))
      - \lambda \delta w_m
    \right. \\ &\hphantom{= \frac{\eqm_m}{2f^\nu} \big[}
    \left. {}
      + (-1)^\nu \prn{ 
        c_m(s) a_m(s) - [\encm \thbm(s)]_m
        - \delta\wm_m - s \delta\etwm_m(s)
        + \lambda a_m(0)
      }
    \right], 
\end{aligned}
\end{equation}
%
where \(\delta\) indicates mean subtraction and \(\eq \mathbf{a}(s) = \hat{A}(s)\).

@@

The Lagrangian we should consider is
%
\begin{equation}\label{eq:lshiftlagrangian}
\begin{aligned}
  \CL =&\, \sum_{ij} \eqm_i \encm_{ij} (\etwm_i - \etwm_j)
        +\sum_{\nu i j}  f^\nu \mu^\nu_{ij}\prn{\MMdm^\nu_{ij} -  s (\eqm_j - \delta_{ij}) }
        &+ \lambda \prn{ \Delta\pr - \sum_i \eqm_i \wm_i },
\end{aligned}
\end{equation}
%
where all of the first-passage times are evaluated at \(s = 0\).

@@

Suppose we have two states, \(i\) and \(j\), with \( \etwm_i > \etwm_j \).
Consider the following perturbation (see also \cref{fig:triangle_s}(\ref{fig:triangle_pert})):
%
\begin{equation}\label{eq:pertKupdn}
\begin{aligned}
  2 \brk{\pdiff{\CL}{\encm_{mj}} - \pdiff{\CL}{\encm_{mi}}}
  &= \frac{1}{f\pot} \brk{\pdiff{\CL}{\MMdm\pot_{mj}} - \pdiff{\CL}{\MMdm\pot_{mi}}} -
  \frac{1}{f\dep} \brk{\pdiff{\CL}{\MMdm\dep_{mj}} - \pdiff{\CL}{\MMdm\dep_{mi}}} \\ 
    &= 2 \eqm_m (\etwm_i - \etwm_j) 
    + \mu\pot_{mj} - \mu\pot_{mi} - \mu\dep_{mj} + \mu\dep_{mi}.
\end{aligned}
\end{equation}
%
Because \( \etwm_i > \etwm_j \), we must have \( \mu\pot_{mi} + \mu\dep_{mj} > 0 \).
So \( \MMdm\pot_{mi} > 0 \) would imply that \( \MMdm\dep_{mj} = 0 \) and vice versa.
These two possibilities are depicted in \cref{fig:triangle_s}(\ref{fig:triangle_left},\ref{fig:triangle_right}).

@@

For any state \(m\), there is a state \(n\) such that all potentiating transitions go to equal or smaller values of \(\etw\) all depressing transitions go to equal or greater values.
%
\begin{equation}\label{eq:separator}
  \forall\ m, \;\; \exists\ n : 
  \begin{cases}
    \etwm_i > \etwm_n &\implies \MMdm\pot_{mi} = 0, \\
    \etwm_i < \etwm_n &\implies \MMdm\dep_{mi} = 0.
  \end{cases}
\end{equation}
%
The remaining allowed transitions from \(m\) are depicted in \cref{fig:triangle_s}(\ref{fig:triangle_allowed}).
Note that we have not yet ruled the possibility that both \( \MMdm\pot_{mn} \) and \( \MMdm\dep_{mn} \) are nonzero.
If one of those transitions is zero, there will be two states with the property above: the targets of right-most depressing and left-most potentiating transitions.

>>>>

If the plasticity events occur at Poisson rate \(r\), the probability of \(n\) events occurring in time \(t\) is given by a Poisson distribution with mean \(rt\).
If we marginalise over \(n\) as well
%
\begin{equation}\label{eq:plastseqav}
\begin{aligned}
  P(\text{state}=i,t \mid \text{pot/dep},0)
    &= \sum_n \frac{(rt)^n}{n!} \e^{-rt} \eq  \MMd \potdep (f\pot \MMd \pot+f\dep \MMd \dep)^n \\
    &= \brk{ \eq  \MMd \potdep\, \e^{rt(f\pot \MMd \pot+f\dep \MMd \dep-\I) } }_i,
\end{aligned}
\end{equation}
%
where \(\eq\) is the steady state distribution of the continuous time transition matrix that appears in the exponential:
%
\begin{equation}\label{eq:eq}
  \eq\frg = 0,
  \qquad\text{where}\quad
  \frg = \sum_\nu r f^\nu (\MMd^\nu - \I)
    = r f\pot \MMd \pot + r f\dep \MMd \dep - r \I.
\end{equation}
%

This results in
%
\begin{equation}\label{eq:overlapwt}
\begin{aligned}
  \av{\synid^1 \syn^1(t)} &= \eq (f\pot \MMd \pot-f\dep \MMd \dep)\, \e^{t\frg} \w, \\
  \av{\synid^1 \syn^1(\infty)} &= \eq (f\pot \MMd \pot-f\dep \MMd \dep)\, \onev\eq \w \\
         &= \eq (f\pot\onev-f\dep\onev)\, \eq \w \\
         &=  (f\pot-f\dep)\, \eq \w \\
         &=  \Delta f\, \eq \e^{t\frg} \w ,
\end{aligned}
\end{equation}
%
where \(\Delta f = f\pot - f\dep \).
Combining the expressions in \cref{eq:overlapwt} allows us to write the numerator of \cref{eq:SNRdef} as
%
\begin{equation}\label{eq:signal}
\begin{aligned}
  \av{\synid \cdt \syn(t)} - \av{\synid \cdt \syn(\infty)}
    &= \frac{N}{r} \eq \enc \, \e^{t \frg} \w , \\
    \text{where} \qquad
  \enc &= \sum_\nu (-1)^\nu r f^\nu (\MMd^\nu - \I)
    = r f\pot \MMd\pot - r f\dep \MMd\dep - r \Delta f \I.
\end{aligned}
\end{equation}
%
Combining with \eqref{eq:noise} gives
%
\begin{equation}\label{eq:SNRcurveExact}
  \SNR(t) = \frac{\sqrt{N} \eq \enc\,\e^{t \frg}\w}
                 {r \sqrt{1-(\Delta f)^2(\eq \w)^2}}.
\end{equation}
%
The denominator will not play any role in what follows, as the models that maximize the various measures of memory performance all have some sort of balance between potentiation and depression, either with \(f\pot=f\dep\) or \(\eq_+=\eq_-\).
We can perform the maximisation in two steps.
First maximise the numerator at fixed \(\eq \w\).
Then maximise the ratio \wrt \(\Delta \pr = \eq\w\).
This will allow us to ignore the denominator until the very end.

We can then treat the off-diagonal elements of \(\MMd^\nu\) as the independent degrees of freedom, subject to these constraints, when maximising the SNR.
The diagonal elements are determined by setting the row sums to 1.
We then have
%
\begin{equation}\label{eq:derivpd}
  \pdiff{\MMdm^\mu_{ij}}{\MMdm^\nu_{mn}} 
      = \delta_{\mu\nu}\, \delta_{im}(\delta_{jn}-\delta_{jm}),
\end{equation}
%
It will also be convenient to define the differential operators
%
\begin{equation}\label{eq:pertfe}
  \pdiff{}{\frgm_{ij}} = \frac{1}{2rf\pot} \pdiff{}{\MMdm \pot_{ij}} + \frac{1}{2rf\dep} \pdiff{}{\MMdm \dep_{ij}},
  \qquad
  \pdiff{}{\encm_{ij}} = \frac{1}{2rf\pot} \pdiff{}{\MMdm \pot_{ij}} - \frac{1}{2rf\dep} \pdiff{}{\MMdm \dep_{ij}},
\end{equation}
%
these satisfy
%
\begin{equation}\label{eq:derivfe}
  \pdiff{\frgm_{ij}}{\frgm_{mn}} = \pdiff{\encm_{ij}}{\encm_{mn}} = \delta_{im}(\delta_{jn}-\delta_{jm}),
  \qquad
  \pdiff{\frgm_{ij}}{\encm_{mn}} = \pdiff{\encm_{ij}}{\frgm_{mn}} = 0.
\end{equation}
%

If we wish to use the off-diagonal elements of \(\frg\) and \(\enc\) as the degrees of freedom, the constraints are
%
\begin{equation}\label{eq:constrfe}
\begin{aligned}
  \frgm_{i \neq j}   &\geq \abs{ \encm_{i \neq j} }, &\qquad
  \sum_{j\neq i}\frgm_{ij} + (-1)^\mu \encm_{ij}  &\leq 2rf^\mu, \\
  \sum_j \frgm_{ij} &=0, &
  \sum_j \encm_{ij} &=0.
\end{aligned}
\end{equation}
%

@@

Now consider the Laplace transform of the SNR curve \eqref{eq:SNRcurveExact}
%
\begin{equation}\label{eq:lsnr}
\begin{aligned}
  A(s) = \intd[_0^{\infty}]{t} \e^{-st}\SNR(t) 
   &= \intd[_0^{\infty}]{t} \frac{ \sqrt{N} \eq \enc \e^{(\frg-s)t} \w }
                                { r\sqrt{1-(\Delta f)^2(\eq\w)^2} } \\
   &= \frac{\sqrt{N} \eq \enc \prn{s \I - \frg}\inv \w }{r\sqrt{1-(\Delta f)^2(\eq\w)^2}}.
\end{aligned}
\end{equation}
%
This expression is ill-behaved at \(s=0\).
Thanks to \eqref{eq:alfund}, we can solve this by the replacement \(\mathbf{G}(s) \to \fund(s)\), as \(\enc\onev=0\).
%
\begin{equation}\label{eq:larea}
\begin{aligned}
  \hat{A}(s) = r A(s) \sqrt{\frac{{{1-(\Delta f)^2(\eq\w)^2}}}{N}}  &=  \eq \enc \fund(s) \w \\
    &= \sum_{ijk} \eqm_i \encm_{ij} \prn{\fptbm_{ik}(s)-\fptbm_{jk}(s)} \eqm_k \wm_k \\
    &= \sum_{ij}  \eqm_i \encm_{ij} (\etwm_{i}(s) - \etwm_{j}(s)).
\end{aligned}
\end{equation}
%
Note that \(A(0)=A\), the area, and \(\lim_{s\to\infty} \brc{sA(s)} = \SNR(0)\), the initial SNR.

@@

In analogy with the case \(s=0\) in \cite{Lahiri2013synapse}, we define
%
\begin{equation}\label{eq:lareacoeffs}
  \begin{aligned}
    {c}_k(s) &= \sum_{ij} \eqm_i \encm_{ij} \prn{\fptbm_{ik}(s)-\fptbm_{jk}(s)}, \\
    {a}_j(s) &= \sum_{k} \encm_{jk} (\etwm_{j}(s) - \etwm_{k}(s)), \\
    \thbm_i(s) &= \sum_j \fptbm_{ij}(0)\, \eqm_j {a}_j(s), \\
  \end{aligned}
    \implies
    \hat{A}(s) 
      % = \sum_k \eqm_k {c}_k(s) \wm_k
      = \mathbf{c}^\dag(s) \w
      = \eq \mathbf{a}(s).
\end{equation}
%
If we regard the \(\wm_k\) as optimisable parameters (limited to the range \( [-1,1] \) wlg.),s the optimal choice is clearly \( \wm_k = \sgn(c_k) \).

Using the same approach as the area bound in \cite{Lahiri2013synapse} we find that the derivatives are
%
\begin{equation}\label{eq:lAdiff}
  \pdiff{\hat{A}(s)}{\MMdm^\mu_{mn}}
     = rf^\mu \eqm_m \prn{ \brk{\thbm_m(s) - \thbm_n(s)}
     +\prn{{c}_m(s) + (-1)^\mu} \brk{\etwm_m(s) - \etwm_n(s)} }.
\end{equation}
%
The term with \(\thb(s)\) comes from differentiating \(\eq\), the term with \(c(s)\) comes from differentiating \(\etw(s)\) and the term with \((-1)^\mu\) comes from differentiating \(\enc\) in \eqref{eq:larea}.

To write down the Hessian, we will first define some notation.
We define the matrix \(\mathbf{X}(s) = \fund(0) \enc \fund(s)\).
Given a four-index array \(H_{ijkl}\), we define \(H\trans_{ijkl} = H_{klij}\).
Then we denote
%
\begin{equation}\label{eq:hessparts}
\begin{alignedat}{2}
    R_{ijkl} &= \smash{\pdiff{\hat{A}}{\frgm_{ij} \circ ; \frgm_{kl}}} &
    &=
    \eqm_i \brc{\fundm_{ik}(0) - \fundm_{jk}(0)} \brc{\thbm_k(s) - \thbm_l(s)} \\
    &&&\hphantom{=} {}
    + \eqm_i \brc{{X}_{ik}(s) - {X}_{jk}(s)} 
          \brc{\etwm_k(s) - \etwm_l(s)} \\
    &&& \hphantom{=} {}
    + \eqm_i {c}_i(s) \brc{\fundm_{ik}(s) - \fundm_{jk}(s)} 
          \brc{\etwm_k(s) - \etwm_l(s)},  \\
  S_{ijkl} &= \smash{\pdiff{\hat{A}}{\encm_{ij} ; \frgm_{kl}} } &
  &= \eqm_k \brc{\fundm_{ki}(0) - \fundm_{li}(0)} \brc{\etwm_i(s) - \etwm_j(s)} \\
    &&& \hphantom{=} {}
    + \eqm_i \brc{\fundm_{ik}(s) - \fundm_{jk}(s)} \brc{\etwm_k(s) - \etwm_l(s)},
\end{alignedat}
\end{equation}
%
where \(R\) contains only those terms where \( \frgm_{ij} \) precedes \( \frgm_{kl} \) in the matrix products from the expression for \( \hat{A} \) in \cref{eq:larea}.
The missing terms sum to \(R\trans\).

Then we can write the Hessian as
%
\begin{equation}\label{eq:hessian}
  \pdiff{^2\hat{A}(s)}{\MMdm^\mu_{ij} \partial \MMdm^\nu_{kl}} =
     r^2 f^\mu f^\nu [R + R\trans + (-1)^\mu S + (-1)^\nu S\trans]_{ijkl}.
\end{equation}
%
This is useful in numerical maximisation.

@@

Consider the Lagrangian
%
\begin{equation}\label{eq:finitelagrangian}
\begin{aligned}
  \CL =&\, \sum_{ij} \eqm_i \encm_{ij} (\etwm_i(s) - \etwm_j(s))
        +\sum_{\nu i j} { r f^\nu \mu^\nu_{ij} \MMdm^\nu_{ij} }
        + \lambda \prn{ \Delta\pr - \sum_i \eqm_i \wm_i },
\end{aligned}
\end{equation}
%
where \(\Delta\pr\) is the constant value we are holding \(\eq\w\) at.
The Karush-Kuhn-Tucker necessary conditions for a maximum are
%
\begin{equation}\label{eq:KTfinite}
  \pdiff{\CL}{\MMdm^\nu_{ij}} = 0, \quad
  \mu^\nu_{ij} \geq 0, \quad
  \pdiff{\CL}{\mu^\nu_{ij}} \geq 0, \quad
  \mu^\nu_{ij}\pdiff{\CL}{\mu^\nu_{ij}} = 0, \quad
  \pdiff{\CL}{\lambda} = 0.
\end{equation}
%
We have scaled the KKT multipliers by \(r f^\nu\) for later convenience.

The derivatives, for \(m \neq n\) are
%
\begin{equation}\label{eq:finitederivs}
\begin{aligned}
  \frac{1}{rf^\nu} \pdiff{\CL}{\MMdm^\nu_{mn}} = & \,
    \eqm_m \prn{ \brk{\thbm_m(s) - \thbm_n(s)}
     + \prn{c_m(s) + (-1)^\nu} \brk{\etwm_m(s) - \etwm_n(s)} } \\
     &+ \mu^\nu_{mn} -  \mu^\nu_{mm}
     + \lambda \eqm_m (\etwm_{m}(0)-\etwm_{n}(0)) 
    = 0.
\end{aligned}
\end{equation}
%
We can solve for the KKT multipliers by noting that
%
\begin{equation*}
  \mu^\nu_{ij} \MMdm^\nu_{ij} = 0,
  \qquad \text{and} \qquad
  \sum_{j: j \neq i} \mu^\nu_{ii} \MMdm^\nu_{ij} 
      = \mu^\nu_{ii} (1 - \MMdm^\nu_{ii}) = \mu^\nu_{ii}.
\end{equation*}
%
Then, with some new vectors defined:
%
\begin{equation}\label{eq:kktsol}
\begin{aligned}
  \mu^\nu_{mm} &= - \eqm_m \prn{ \albm^\nu_m(s) 
    + \lambda \ombm^\nu_m(0) 
    + \prn{{c}_m(s) + (-1)^\nu} \ombm^\nu_m(s)
    }, \\
  \mu^\nu_{mn} &= \eqm_m \big( 
      \brk{ \thbm_n(s) - \thbm_m(s) - \albm^\nu_m(s) }
    + \lambda \brk{ \etwm_n(0) - \etwm_m(0) - \ombm^\nu_m(0) } 
  \\ &\hphantom{= \eqm_m \big( }
    + \brk{{c}_m(s) + (-1)^\nu} 
        \brk{ \etwm_n(s) - \etwm_m(s) - \ombm^\nu_m(s) }
     \big), \\
  \text{where} \quad 
  \alb^\nu(s) &= (\MMd^\nu - \I) \thb(s), \qquad
  \omb^\nu(s) = (\MMd^\nu - \I) \etw(s).
\end{aligned}
\end{equation}
%
If we note that we can write \( \MMd^\nu - \I = \prn{\frg + (-1)^\nu \enc} / 2rf^\nu \), we find that
%
\begin{equation}\label{eq:diagKKT}
\begin{aligned}
  \alb^\nu(s) &= \frac{\delta\mathbf{a}(s) + (-1)^\nu \enc \thb(s)}
                     {2rf^\nu},
  \qquad 
  \omb^\nu(s) = \frac{\delta\w + s \delta\etw(s) - (-1)^\nu \mathbf{a}(s)}
                     {2rf^\nu}, 
  \\
  \mu^\nu_{mm} &= \frac{\eqm_m}{2rf^\nu} 
    \left[ 
      \hat{A}(s) - c_m(s) (\delta\wm_m + s \delta\etwm_m(s))
      - \lambda \delta w_m
    \right. \\ &\hphantom{= \frac{\eqm_m}{2f^\nu} \big[}
    \left. {}
      + (-1)^\nu \prn{ 
        c_m(s) a_m(s) - [\encm \thbm(s)]_m
        - \delta\wm_m - s \delta\etwm_m(s)
        + \lambda a_m(0)
      }
    \right], 
\end{aligned}
\end{equation}
%
where \(\delta\) indicates mean subtraction and \(\eq \mathbf{a}(s) = \hat{A}(s)\).

@@

The Lagrangian we should consider is
%
\begin{equation}\label{eq:lshiftlagrangian}
\begin{aligned}
  \CL =&\, \sum_{ij} \eqm_i \encm_{ij} (\etwm_i - \etwm_j)
        +\sum_{\nu i j} r f^\nu \mu^\nu_{ij}\prn{\MMdm^\nu_{ij} -  s (\eqm_j - \delta_{ij}) }
        &+ \lambda \prn{ \Delta\pr - \sum_i \eqm_i \wm_i },
\end{aligned}
\end{equation}
%
where all of the first-passage times are evaluated at \(s = 0\).

@@

Suppose we have two states, \(i\) and \(j\), with \( \etwm_i > \etwm_j \).
Consider the following perturbation (see also \cref{fig:triangle_s}(\ref{fig:triangle_pert})):
%
\begin{equation}\label{eq:pertKupdn}
\begin{aligned}
  2 \brk{\pdiff{\CL}{\encm_{mj}} - \pdiff{\CL}{\encm_{mi}}}
  &= \frac{1}{rf\pot} \brk{\pdiff{\CL}{\MMdm\pot_{mj}} - \pdiff{\CL}{\MMdm\pot_{mi}}} -
  \frac{1}{rf\dep} \brk{\pdiff{\CL}{\MMdm\dep_{mj}} - \pdiff{\CL}{\MMdm\dep_{mi}}} \\ 
    &= 2 \eqm_m (\etwm_i - \etwm_j) 
    + \mu\pot_{mj} - \mu\pot_{mi} - \mu\dep_{mj} + \mu\dep_{mi}.
\end{aligned}
\end{equation}
%
Because \( \etwm_i > \etwm_j \), we must have \( \mu\pot_{mi} + \mu\dep_{mj} > 0 \).
So \( \MMdm\pot_{mi} > 0 \) would imply that \( \MMdm\dep_{mj} = 0 \) and vice versa.
These two possibilities are depicted in \cref{fig:triangle_s}(\ref{fig:triangle_left},\ref{fig:triangle_right}).

@@

For any state \(m\), there is a state \(n\) such that all potentiating transitions go to equal or smaller values of \(\etw\) all depressing transitions go to equal or greater values.
%
\begin{equation}\label{eq:separator}
  \forall\ m, \;\; \exists\ n : 
  \begin{cases}
    \etwm_i > \etwm_n &\implies \MMdm\pot_{mi} = 0, \\
    \etwm_i < \etwm_n &\implies \MMdm\dep_{mi} = 0.
  \end{cases}
\end{equation}
%
The remaining allowed transitions from \(m\) are depicted in \cref{fig:triangle_s}(\ref{fig:triangle_allowed}).
Note that we have not yet ruled the possibility that both \( \MMdm\pot_{mn} \) and \( \MMdm\dep_{mn} \) are nonzero.
If one of those transitions is zero, there will be two states with the property above: the targets of right-most depressing and left-most potentiating transitions.
Note that we have not yet proved anything about where \(\etwm_m\) lies with respect to any of the others.
